Programming Assignment 2

### 2015-04-02 paper.tex
Update paper.tex
Added content to the HAMMING/MAX section

\section{Hamming-Max Network}

@@

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section? or perhaps the LVQ

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM

\subsection{Skyler Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

@@

\subsubsection{Project Presentation}
lulz he ain't done a thing.

@@

\subsubsection{Project Presentation}
nuthin.

>>>>

\section{Hamming-Max Network}
The Hamming-Max was fairly straight forward to construct.  We first created the hammingnet portion which was given the input vector and weight matrix.  It computed the hamming distance of the input from each column vector prototype of the weight matrix, storing those values in an output vector, equal in width to the weight matrix.  We then constructed the Maxnet which was given the Hammingnet output as a parameter.  It subtracts 1 from each element until a single zero value is found, declaring it the smallest hamming distance.  This index represents the prototype which is most similar to the input, suggesting the input must be of this classification.

\subsection{Image Encoding}
Deciding how to encode our images was a bit tricky.  We played with a few different ways of obtaining image outlines however, we decided for this network, simply finding images already in outline form would be best.  We removed inner detail from these outlines and ran them through a program we wrote.  First, the images are resized so that they are all one standard size,  the images are then grayscaled and run through a threshhold function so that a clear outline of black on white is present.  To establish the prototypes for our weight matrix, we added the values of each representative image matrix to eachother, then averaged the values and processed the result as before.  We adjusted our threshhold function to maintain clarity.  We found that visually, too small a size diminshed image definition, while too large was time and resource intensive and lacked definitive shape for the prototype matrix.

@@

\subsubsection{Project Report}
Jonathan was tasked with the Hamming/Max section.

\subsubsection{Project Presentation}
NOTHING HE DID NOTHING 0 percent FOR HIM....DAMN YOU SKYLER

\subsection{Skyler "Scrub" Manzanares}
\subsubsection{Programming}
Skyler implemented the formatting of centroid images to the weight matrix to be fed into the Hamming/MAX network. He also did extensive work creating the functions that read in and format images. Skyler was also responsible for implementing
the HAM network.

@@

\subsubsection{Project Presentation}
lulz he ain't done a thing.  0\% for you

@@

\subsubsection{Project Presentation}
nuthin. no soup for you
